Uncertainty Quantification in Multiscale Models of Charge Transport in Organic Semiconductors: Influence of the Exhange-Correlation Functional

### 2024-11-29 paper.tex
first pass at the intro

\begin{abstract}
  This work quantifies uncertainties in a multiscale model for charge dynamics in organic semiconductors (OSCs). A first-principle multiscale model integrates classical molecular dynamics (MD), density functional theory (DFT), quantum mechanical calculation and continuous-time random walk (CTRW) processes to allow the simulation of charge transport in OSCs. The model brings inherent uncertainties arising from the empirical approximations and numerical simulations. Our work particularly focusing on quantifying the uncertainty in DFT exchange-correlation functional.

@@

\section{Introduction}

\bjoern{Intro OSCs}{to adjust}In this work, an investigated model containing uncertainties is the multiscale model of charge dynamics~\cite{Baumeier2011, edeling_global_2024,coropceanu_charge_2007} in organic semiconductors (OSCs), which are materials that consist of organic molecules with disordered and amorphous structure. Besides its semiconducting properties, they are mechanically flexible and comes with controllable charge transport properties~\cite{hamers_flexible_2001,liu_high_2015,chow_organic_2020}. 
This flexible functionality is achieved by tuning molecular properties to achieve an ideal operating properties at the device-level\cite{bronstein_role_2020, bredas_organic_2002}, so a fundamental understanding of OSC from molecule scale  plays an important role in OSC optimization.
Conducting these optimization processes through experimental methods is financially demanding. In contrast, computational approaches such as the multiscale model provides insightful guidance for such investigation. So robustness of the computational model is paramount to promote OSC optimization.

\bjoern{Idea of the Multiscale Model}{}Like every other models, the multiscale model contains uncertainties due to certain approximation in modeling perspective, the randomness nature of the physical quantities, and the limitation of the numerical simulations, only to name a few.
To explain in detail those uncertainties, the first-principle multiscale model is briefly reviewed.

Fundamentally, quantum-mechanical description is needed to model charge dynamics due to the motion of electrons. However, the resulting full many-electron schr\"{o}dinger equation is impossible to solve due to its complexity, so Density Functional Theory (DFT) \cite{kohn_selfconsistent_1965,jones_density_2015, hammesschiffer_conundrum_2017} appears as a manageable way to model electrons.
DFT has its own challenges in achieving multiscale modeling.
The first challenge relates to the Born-Oppenheimer approximation \cite{born_zur_1927} in quantum
mechanics, which simplifies the problem by separating the electronic and nuclear
coordinates. As a result, the time evolution of the atomic coordinates can be modeled in molecular dynamics (MD) by solving the Newton's equation using empirical force field to approximate the potential energy surfaces~\cite{rapaport_art_2004}.

The next challenge is the infeasibility of solving the DFT equations for the entire system even at a fixed time~\cite{hammesschiffer_conundrum_2017}. 
But due to fact that OSCs have disordered and amorphous structure and the quantum states of each molecule is confined to a limited region, the charge dynamic can be well-approxmiated as a jumping process between molecules, which is a continuous time random walk (CTRW) process.
The transition rates between the molecules can be calculated from quantum chemical calculations and related to the electronic structures parameters including the molecule energy, reorganization energy and coupling elements which will be explained in the methodology section.

Until this point, the molecular system is modeled as graph $\mathbf{G}(\mathbf{V}, \mathbf{W})$ where $\mathbf{V}$ is the set of nodes and $\mathbf{W}: \omega_{ij}$ is the adjacency matrix. Each node represents one molecule, the weighted and directed edge $\omega_{ij}$ represents the transition rates from node $i$ to node $j$ calculated from quantum chemical methods. 
As will be shown in the method section, $\omega_{ij}$ determines the QoIs whose quantities we want to quantify.

Figure \ref{fig:MSM} summarized the multiscale model as mentioned above using MADN, a type of OSC as an example. 
The process includes: Firstly, classical Molecular Dynamics is used to generate the atomistic coordinates of all molecules. Then DFT is used to obtain electronic structures. Finally the charge dynamic is model as a CTRW among the molecules.

\bjoern{UQ in general}{}
Theoretical model and computer simulation for understanding a physical system usually contain some uncertainties in predicting the system features. 
For example, the theoretical model does not encompass all relevant physical factors, the theoretical model incorporates empirical parameters that include noise, the numerical scheme contains approximation, the simulation use noisy quantities, etc~\cite{sarkar_uncertainty_2017,oconnor_quantifying_2024, chernatynskiy_uncertainty_2013, suleimenova_tutorial_2021,coveney_reliability_2021, coveney_when_2021}.
Nevertheless, those uncertainties should not affect the validity of the model or the accuracy for the predicting system in terms of some quantities of interest (QoI). 
Here the terminology "uncertainties" refers to the impossibility of getting a deterministic QoI, and excludes theoretical or numerical errors. 
The amount of uncertainty in the QoI plays an important role in determining the usefulness of the model. 
So quantifying the uncertainty is a key factor for telling if the model is quanlitatively or quantitatively accurate.

@@

\bjoern{Uncertainties in the MSM}{way too verbose}
In achieving the multiscale model, uncertainties are introduced. 
While Born-Oppenheimer approximation allows for the use of force field to approximate the potential energy surfaces and model the atomic coordinates using Newton’s equations, the force field is not exactly the same as the potential for DFT~\cite{izvekov_effective_2004}. 
So the atomic coordinates, that is the molecule structures contain uncertainty which ultimately affects the charge dynamics. 
This is one source of uncertainty that have not been investigated. But in our investigation, a fixed molecule structure is used and we do not consider this source of uncertainty. 
Secondly, charge jumping between the state localization is not exactly a time dependent DFT process. 
However, the amorphous OSCs used in this work has strong disorder, so the model noise from state localization is negligible and we do not consider the uncertainty originated from this perspective.

\bjoern{Focus on functional dependence}{should talk about the sensitivity of the functional first, then say that looking at HFX is a 'single-parameter' study.} Lastly, the source of uncertain that this work focus on comes from the approximation for the exchange-correlation energy in DFT. 
There is no exact formula for the exchange-correlation functional, so in practical approximations are developed and tested to guarantee the robustness of DFT method~\cite{gunnarsson_exchange_1976, bilc_hybrid_2008, lee_development_1988}. 
The accuracy of DFT depends heavily on the choice of the exchange-correlation functional whose suitability is usually unknown for new synthesized molecules. 
As an advancement to improve accuracy, Hybrid-DFT \cite{marques_densitybased_2011,perdew_rationale_1996} incorporates a portion $\alpha$ of exact HF exchange functional (HFX) from Hartree-Fock (HF) theory into the exchange-correlation functional, particularly for systems where DFT falls short. For example, the PBE0 functional has a portion of 0.25 HFX~\cite{adamo_toward_1999}.

Looking back into the CTRW of the charge transport, the transition rates depend on the electronic structures parameters which rely on the validity of the exchange-correlation functional from the modeling perspectives.
So the approximations in exchange-correlation functional will bring uncertainties to the multiscale model~\cite{medvedev_density_2017}. 
In particular, different hybrid-DFT functionals containing varying HFX levels will generate different output from the multiscale model mentioned aboved. 
The effect of such uncertainty from the electronic structure level on the multiscale model is not yet explored in literatures. 
The goal of this work is to quantify the uncertainty effect of the exchange-correlation functional on the charge dynamics in OSCs and to study the robustness of the multiscale model, with a particular focus on the uncertainty represented by different portional of HFX.

\bjoern{Definition of a QoI}{is ToF (mobility)} A QoI need be chosen to perform this goal of uncertainty quantification. 
The figure of merit in OSC investigation is the charge mobility, which quantitatively describe how fast charges move in an OSC. 
The charge mobility is commonly measured in a \textit{time-of-flight} (ToF) setting. 
As shown in Fig.\ref{fig:MSM}(d), charge carriers are injected into one electrode called \textit{Source} and they are collected by another electrode at the opposite end called \textit{Sink}. 
Knowing the length of the sample $L$ and the time-of-flight $\tau$, the diffusive velocity is calculated as $v_\text{ToF}=\frac{L}{\tau}$.
When electric field $\vec{F}$ is used and the charge dynamics undergo a field-drifted transport, the charge mobility is calculated as $\mu_\text{ToF}=\frac{\vec{v}_\text{ToF} \vec{F}}{|\vec{F}|^2}$.

%Some literatures also report a steady state setting for investigation of charge mobility. In such condition, there is no \textit{Source}-\textit{Sink} boundary condition. Instead, the molecular system is infinitely repeated in all three dimensions by periodic boundary conditions. 
%Over a long time period, the charge occupation on each molecule $\pi_i$ reach an equilibrium, allowing a steady state distribution to be obtained.
%The steady state charge velocity $v_\text{SS}$ is calculated as the charge velocity along the direction of the electric field normalized by the steady state charge occupation $\vec{\pi}:\pi_i$. 
%The calculation for $v_\text{ToF}$ and $\mu_\text{SS}$ will be detailed in the method section.

\bjoern{Rephrase}{!}To quantify the uncertainty for QoI, the focus of our work will be placed on answering the following questions: 
\begin{enumerate}
    \item How does HFX level change the electronic structures: reorganization energy, distribution of molecule energies and coupling elements? 
    \item How does HFX level change the charge mobility?
    \item Which electronic structure (among energy, coupling element and reorganization energy) uncertainty has the most impact on the QoI distribution?
    \item Can we estimate the range of the QoI, given a confidence level?
\end{enumerate}

\bjoern{Update}{later} The rest of the paper is organized as follows. Section 2 will outline the multiscale model in OSCs. This includes the electronic structure calculation centering on Kohn-Sham equation, the calucation of molecule energy, reorganization energy and coupling elements. The details of the molecule dynamics to obtain the MADN system will be listed.
Then section 3 present the multiscale modeling results with the chosen HFX values. In section 4, the Monte Carlo sampling method is utilized to estimate the ToF distribution and $v_\text{SS}$ distribution, followed by the sensitivity analysis on the parameters. 
Section 5 shows calculated Poole-Frankel behavior of the MADN with varying HFX values. The confidence interval of the Poole-Frankel plot is estimated. Section 6 concludes the paper.

\section{Multiscale Model}
As mentioned in the introduction, the multiscale model maps a structural morphology into a graph $\mathbf{G}(\mathbf{V}, \mathbf{W})$. In our context, the graph properties, that is the entries $\omega_{ij}$ in the adjacency matrix $\mathbf{W}$, only depends on the HFX values since other modeling parameters are kept consistent.

Those transition rates charge transfer rates from molecules $i$ to $j$ is calculated as the bi-molecular transition rates:
%
\begin{equation}
    \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{ij}|^2}{\sqrt{4\pi \lambda_{ij} k_\text{B}T}} \exp\left(-\frac{(\Delta E_{ij} + q \vec{F} \cdot \vec{r}_{ij} - \lambda_{ij})^2}{4\lambda_{ij} k_\text{B}T}\right) ,
    \label{equ:Marcus}
\end{equation}
%
where $\hbar$ is the reduced Planck constant and $k_\text{B}$ the Boltzmann constant. The temperature $T$ (in \unit[]{K}), the charge of the carrier $q$ (in \unit[]{e}) and the external electric field $\vec{F}$ (in V/m) can be considered the external, environmental parameters of the simulation. The vector $\vec{r}_{ij} = (r^x_{ij},r^y_{ij},r^z_{ij})^\text{T}$ connects the center-of-masses (COMs) of molecules $i$ and $j$, which is calculated using cyclic boundary conditions. 
The remaining physical, material-specific (or rather transfer-pair-specific) quantities are the reorganization energy $\lambda_{ij}$, the electronic coupling $J_{ij}$, and the energy difference $E_{ij} = E_i - E_j$ (all in \unit[]{eV}). 
In our model, two nodes $i,j$ form a connection of the corresponding molecules $i,j$ have their closest-contact distance smaller than $r_\text{cutoff}=\unit[0.5]{nm}$.
The rest of this section will introduce the following: the molecular dynamics used to obtain the coordinates $r^x_{i},r^y_{i},r^z_{i}$, the calculation of node-specific quantities $\lambda$, $E_i$ and $J_{ij}$, as well as the calculation of ToF $\tau$ and steady state velocity $v_\text{SS}$.

@@

\section{Results on MADN}

In this study, we investigate the hole-transporting organic semiconductor MADN (2-Methyl-9,10-di(naphth-2-yl)anthracene) and study its charge mobility's dependence on HFX.

@@

To demonstration the effect of HFX on the atomic charges and molecule polarizability $P_\text{iso}$,Figure \ref{fig:autogen_MADN}(a)(b) illustrates the dependence of the dipole moment $\mu$ and isotropic polarizability $P_\text{iso}$ on HFX.
Figure \ref{fig:autogen_MADN}(c)(d) show 
The reorganization energy $\lambda$ and energy disorder $\sigma(E)$ as a function of HFX parameter are also shown in Fig.~\ref{fig:autogen_MADN}(c)(d).

@@

The ToF is also calculated without energy disorder, meaning $\Delta E_{ij}=0$ for all $i,j$.
Table \ref{tab:ToF_MADN_HFX} shows the ToF and corresponding diffusive velocity $v_\text{ToF}$.
With energy disorder, the ToF increases by a factor of approximately 15 as $\alpha$ increases from 0 to 0.25.  
While without energy disorder, the increase factor is about 4. This increase in ToF is attributed to the rise in $\lambda$, changes in molecular energies, and variations in coupling elements.

\begin{table}[tbp]%The best place to locate the table environment is directly after its first reference in text
\caption{\label{tab:ToF_MADN_HFX}%
The ToF and diffusive velocity calculated by ToF along a distance $L_x = \unit[9.0]{nm}$ with and without energy disorder of the MADN system as a function of the HFX. The ToF is in unit $\unit[]{s}$ and $v_\text{ToF}$ in unit $\unit[]{m/s}$.
}
\begin{ruledtabular}
  \begin{tabular}{c c c c c}
        $\alpha$ & ToF& $v_\text{ToF}$ & ToF(no $E$)& $v_\text{ToF}$(no $E$) \\
    \hline
        0.00 &  $6.4 \times 10^{-9}$ & 1.2 & $1.9 \times 10^{-10}$ & 42 \\
        0.05 & $ 7.9 \times 10^{-9}$ & 1.0 & $4.1 \times 10^{-10}$ & 20 \\
        0.10 & $ 1.6 \times 10^{-8}$ & 0.51 & $4.0 \times 10^{-10} $ & 20 \\
        0.15 & $ 3.0 \times 10^{-8}$ & 0.31 & $4.0 \times 10^{-10} $ & 25 \\
        0.20 & $ 2.1 \times 10^{-8}$ & 0.39 & $4.5 \times 10^{-10}$ & 18 \\
        0.25 & $ 9.5 \times 10^{-8}$ & 0.083 & $7.2 \times 10^{-10}$ & 11 \\
    \end{tabular}
\end{ruledtabular}
\end{table}

%
\begin{table*}[tbp]%The best place to locate the table environment is directly after its first reference in text
\caption{\label{tab:W2_E}%
The 1-Wasserstein distance between the distributions pair of molecule energy $P_{E(\alpha)}$, electrostatic energy $P_{E^\text{el}(\alpha)}$, polar energy $P_{E^\text{polar}(\alpha)}$ and $P_{\log_{10}(J_{ij}^2)(\alpha)}$.
}
\begin{ruledtabular}
  \begin{tabular}{c c c c c c}
  $\alpha'$ & 0 & 0.05 & 0.10 & 0.15 & 0.20 \\
    \hline
  $W_1 (P_{E(\alpha')}, P_{E(\alpha=0.25)})$ &  0.0054 & 0.0091 & 0.0067 & 0.0053 & 0.0045 \\
  $W_1 (P_{E^\text{el}(\alpha')}, P_{E^\text{el}(\alpha=0.25)})$ &  0.010 & 0.012 & 0.0089 & 0.0070 & 0.0032 \\
  $W_1 (P_{E^\text{polar}(\alpha')}, P_{E^\text{polar}(\alpha=0.25)})$ &  0.0065 & 0.0043 & 0.0027 & 0.0023 & 0.0031 \\
  $W_1 (P_{\log_{10}(J_{ij}^2)(\alpha')}, P_{\log_{10}(J_{ij}^2)(\alpha=0.25)})$ &  0.0054 & 0.0091 & 0.0067 & 0.0053 & 0.0045 \\
    \end{tabular}
\end{ruledtabular}
\end{table*}
%

@@

\section{ToF Distribution and Sensitivity Analysis}
The previous section shows that different HFX affect the calculated ToF. In this section, we use the Monte Carlo method to estimate the range of the ToF given a confidence level, followed by a sensitivity analysis to determine which parameter contributes more to the variance of ToF.

>>>>

\begin{abstract}
  \bjoern{TODO}{rewrite}This work quantifies uncertainties in a multiscale model for charge dynamics in organic semiconductors (OSCs). A first-principle multiscale model integrates classical molecular dynamics (MD), density functional theory (DFT), quantum mechanical calculation and continuous-time random walk (CTRW) processes to allow the simulation of charge transport in OSCs. The model brings inherent uncertainties arising from the empirical approximations and numerical simulations. Our work particularly focusing on quantifying the uncertainty in DFT exchange-correlation functional.

@@

\section{Introduction}
Organic semiconductors (OSCs) are materials that consist of organic molecules, often in disordered structures formed during spin-coating or deposition processing. Besides their semiconducting properties, they are mechanically flexible and come with the potential to control charge transport properties~\cite{hamers_flexible_2001,liu_high_2015,chow_organic_2020}. This flexible functionality is achieved by tuning molecular properties to achieve an ideal operation at the device level~\cite{bronstein_role_2020, bredas_organic_2002}. Computational approaches that aim at predicting the charge transport properties of disordered molecular materials resolving the interplay between single-molecule properties (such as their electronic structure or response properties) and mesoscale material morphology can play an important role in supporting or even guiding experimental optimization processes.\bjoern{add citations}{}

@@

First-principles based multiscale models are such types of computational approaches. Due to the infeasibility of explicitly simulating the coupled non-adiabatic electron-nuclear dynamics for the time- and length scales of realistic materials, these models typically exploit the localization of electronic states in disordered molecular materials and consider a rate-based description of hopping-type transport. A popular choice for the electron transfer rate $\omega_{ij}$ between two localization sites $i$ and $j$ is Marcus theory~\bjoern{add}{citation}, in which
%
\begin{equation}
    \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{ij}|^2}{\sqrt{4\pi \lambda_{ij} k_\text{B}T}} \exp\left(-\frac{(\Delta E_{ij} - \lambda)^2}{4\lambda k_\text{B}T}\right) ,
    \label{equ:Marcus}
\end{equation}
%
where $\hbar$ is the reduced Planck constant,  $k_\text{B}$ the Boltzmann constant, and $T$ the temperature. As depicted in Fig.~\ref{fig:MSM}, given a larger scale morphology and with the definition of localization sites (Fig.~\ref{fig:MSM}(a)), multiscale models employ first-principles based methods (Fig.~\ref{fig:MSM}(b)) to explicitly calculate the remaining physical, material-specific (or rather transfer-pair-specific) quantities in Eq.~\ref{equ:Marcus}: the reorganization energy $\lambda$ (here a single value as we assume a single-component material), the electronic coupling $J_{ij}$, and the site energy difference $\Delta E_{ij} = E_i - E_j$. With all that information, charge transport is modeled as a continuous time random walk (CTRW) process on a graph $\mathbf{G}$, constructed from the localization sites and the calculated rates between them (Fig.~\ref{fig:MSM}(c)). Panel (b) of Fig.~\ref{fig:MSM} mentions some specific methods for the calculation of the quantities entering Eq.~\ref{equ:Marcus}, such as mixed quantum-classical methods for obtaining the site energies with the help of microelectrostatic methods \bjoern{add}{citations} or the dimer projection method for determining coupling elements~\cite{baumeier_density_2010}, as they are the ones adopted in this work. What is essential about these and alternative ones is that they typically rely on density-functional theory (DFT) calculations, either directly or as a mean to parametrize classical models. The dependence of DFT calculations on the choice of an exchange-correlation functional raises the question of how sensitive the simulated charge transport is to this choice and how certain predictions of material properties are.

Uncertainty quantification (UQ) is concept from computational science which allows for an estimation of confidence intervals for a quantity of interest (QoI) and an analysis of its sensitivity in models of a physical system that contain uncertain, maybe empirical, or noisy, parameters~\cite{sarkar_uncertainty_2017,oconnor_quantifying_2024, chernatynskiy_uncertainty_2013, suleimenova_tutorial_2021,coveney_reliability_2021, coveney_when_2021}. Many common UQ studies focus on models with (partial) differential equations, e.g., drift-diffusion equations in which the diffusivity as parameter, and assume a certain distribution for the values of the parameter(s). For the multiscale model of charge transport, it is not straightforward to cast the large variety of available exchange-correlation functionals into the role of a model parameter with some distribution. To keep the problem tractable, we focus here instead specifically on the exchange part in hybrid functionals~\cite{perdew_rationale_1996,marques_densitybased_2011}, in which a DFT model for the exchange is mixed using a weighting factor $\alpha_\text{HFX}$ with a Hartree--Fock type exchange, i.e.,
%
\begin{equation}
  E_\text{x} = \alpha_\text{HFX} E_\text{x}^\text{HF} + (1-\alpha_\text{HFX})E_\text{x}^\text{DFT}.
  \label{equ:hybrid}
\end{equation}
%
More specifically, we take as the basis the PBE0 functional~\cite{adamo_toward_1999} and scrutinize (i) how the predictions of the multiscale model of charge transport are affected by variation of $\alpha_\text{HFX}$ as a proxy for uncertainties in the choice of DFT functionals, (ii) what the level of confidence is in quantitative predictions, and (iii) what are the most sensitive quantities in the model. In this sense, Eq.~\ref{equ:hybrid} is deceptively simple. For each value of $\alpha_\text{HFX}$, the graph $G$ is constructed using the respective value of the reorganization energy, the $N_\text{mol}$ site energies, and the $N_\text{pair}$ coupling elements, and the dimensionality of the problem from the perspective of UQ is $N_\text{UQ}=1+N_\text{mol}+N_\text{pair}$, which can easily be on the order of $10^{4}-10^{5}$. We consider the simulated time-of-flight (ToF) and the associated mobility the QoI in the following (see Fig.~\ref{fig:MSM}(c)) which then are subject to uncertainties in these $N_\text{UQ}$ parameters, {\em stemming} from the variation in $\alpha_\text{HFX}$. As a prototypical system, we will study hole transport in an amorphous morphology of 2-methyl-9, 10-bis(naphthalen-2-yl)anthracene (MADN), a wide-gap semiconductor that is used extensively as an ambipolar host material in organic light-emitting diodes~\bjoern{add}{citation}.

This paper is organized as follows. Section~\ref{sec:model} outlines the theoretical and computational details of the multiscale model, including the morphology simulation with classical molecular dynamics, the determination of all quantities in the transition rates, and the calculation of the charge transport properties from the constructed graph model. In Section~\ref{sec:MSMresults}, we discuss the explicit results from the model using different values of $\alpha_\text{HFX}$, before we show the results of uncertainty quantification and sensitivity analysis via Monte Carlo sampling. A brief summary concludes the paper.

\section{Multiscale Model}
\label{sec:model}
As mentioned in the introduction, the multiscale model maps a structural morphology into a graph $\mathbf{G}(\mathbf{V}, \mathbf{W})$. In our context, the graph properties, that is the entries $\omega_{ij}$ in the adjacency matrix $\mathbf{W}$, only depends on the HFX values since other modeling parameters are kept consistent.

Those transition rates charge transfer rates from molecules $i$ to $j$ is calculated as the bi-molecular transition rates:
%
\begin{equation}
    \omega_{ij} = \frac{2\pi}{\hbar} \frac{|J_{ij}|^2}{\sqrt{4\pi \lambda_{ij} k_\text{B}T}} \exp\left(-\frac{(\Delta E_{ij} + q \vec{F} \cdot \vec{r}_{ij} - \lambda_{ij})^2}{4\lambda_{ij} k_\text{B}T}\right) ,
    \label{equ:Marcus2}
\end{equation}
%
where $\hbar$ is the reduced Planck constant and $k_\text{B}$ the Boltzmann constant. The temperature $T$ (in \unit[]{K}), the charge of the carrier $q$ (in \unit[]{e}) and the external electric field $\vec{F}$ (in V/m) can be considered the external, environmental parameters of the simulation. The vector $\vec{r}_{ij} = (r^x_{ij},r^y_{ij},r^z_{ij})^\text{T}$ connects the center-of-masses (COMs) of molecules $i$ and $j$, which is calculated using cyclic boundary conditions. 
The remaining physical, material-specific (or rather transfer-pair-specific) quantities are the reorganization energy $\lambda_{ij}$, the electronic coupling $J_{ij}$, and the energy difference $E_{ij} = E_i - E_j$ (all in \unit[]{eV}). 
In our model, two nodes $i,j$ form a connection of the corresponding molecules $i,j$ have their closest-contact distance smaller than $r_\text{cutoff}=\unit[0.5]{nm}$.
The rest of this section will introduce the following: the molecular dynamics used to obtain the coordinates $r^x_{i},r^y_{i},r^z_{i}$, the calculation of node-specific quantities $\lambda$, $E_i$ and $J_{ij}$, as well as the calculation of ToF $\tau$ and steady state velocity $v_\text{SS}$.

@@

\section{Results on MADN}
\label{sec:MSMresults}
In this study, we investigate the hole-transporting organic semiconductor MADN (2-Methyl-9,10-di(naphth-2-yl)anthracene) and study its charge mobility's dependence on HFX.

@@

To demonstration the effect of HFX on the atomic charges and molecule polarizability $P_\text{iso}$, Fig.~\ref{fig:autogen_MADN}(a)(b) illustrates the dependence of the dipole moment $\mu$ and isotropic polarizability $P_\text{iso}$ on HFX. Figure~\ref{fig:autogen_MADN}(c)(d) show the reorganization energy $\lambda$ and energy disorder $\sigma(E)$ as a function of HFX parameter are also shown in Fig.~\ref{fig:autogen_MADN}(c)(d).

@@

The ToF is also calculated without energy disorder, meaning $\Delta E_{ij}=0$ for all $i,j$.
Table~\ref{tab:ToF_MADN_HFX} shows the ToF and corresponding diffusive velocity $v_\text{ToF}$.
With energy disorder, the ToF increases by a factor of approximately 15 as $\alpha$ increases from 0 to 0.25.  
While without energy disorder, the increase factor is about 4. This increase in ToF is attributed to the rise in $\lambda$, changes in molecular energies, and variations in coupling elements.

\begin{table}[tbp]
\caption{The ToF and diffusive velocity calculated by ToF along a distance $L_x = \unit[9.0]{nm}$ with and without energy disorder of the MADN system as a function of the HFX. The ToF is in unit $\unit[]{s}$ and $v_\text{ToF}$ in unit $\unit[]{m/s}$.}
\begin{ruledtabular}
  \begin{tabular}{c c c c c}
        $\alpha$ & ToF& $v_\text{ToF}$ & ToF(no $E$)& $v_\text{ToF}$(no $E$) \\
    \hline
        0.00 &  $6.4 \times 10^{-9}$ & 1.2 & $1.9 \times 10^{-10}$ & 42 \\
        0.05 & $ 7.9 \times 10^{-9}$ & 1.0 & $4.1 \times 10^{-10}$ & 20 \\
        0.10 & $ 1.6 \times 10^{-8}$ & 0.51 & $4.0 \times 10^{-10} $ & 20 \\
        0.15 & $ 3.0 \times 10^{-8}$ & 0.31 & $4.0 \times 10^{-10} $ & 25 \\
        0.20 & $ 2.1 \times 10^{-8}$ & 0.39 & $4.5 \times 10^{-10}$ & 18 \\
        0.25 & $ 9.5 \times 10^{-8}$ & 0.083 & $7.2 \times 10^{-10}$ & 11 \\
    \end{tabular}
\end{ruledtabular}
\label{tab:ToF_MADN_HFX}
\end{table}

\begin{table*}[tbp]%The best place to locate the table environment is directly after its first reference in text
\caption{\label{tab:W2_E}%
The 1-Wasserstein distance between the distributions pair of molecule energy $P_{E(\alpha)}$, electrostatic energy $P_{E^\text{el}(\alpha)}$, polar energy $P_{E^\text{polar}(\alpha)}$ and $P_{\log_{10}(J_{ij}^2)(\alpha)}$.
}
\begin{ruledtabular}
  \begin{tabular}{c c c c c c}
  $\alpha'$ & 0 & 0.05 & 0.10 & 0.15 & 0.20 \\
    \hline
  $W_1 (P_{E(\alpha')}, P_{E(\alpha=0.25)})$ &  0.0054 & 0.0091 & 0.0067 & 0.0053 & 0.0045 \\
  $W_1 (P_{E^\text{el}(\alpha')}, P_{E^\text{el}(\alpha=0.25)})$ &  0.010 & 0.012 & 0.0089 & 0.0070 & 0.0032 \\
  $W_1 (P_{E^\text{polar}(\alpha')}, P_{E^\text{polar}(\alpha=0.25)})$ &  0.0065 & 0.0043 & 0.0027 & 0.0023 & 0.0031 \\
  $W_1 (P_{\log_{10}(J_{ij}^2)(\alpha')}, P_{\log_{10}(J_{ij}^2)(\alpha=0.25)})$ &  0.0054 & 0.0091 & 0.0067 & 0.0053 & 0.0045 \\
    \end{tabular}
\end{ruledtabular}
\end{table*}
%

@@

\section{ToF Distribution and Sensitivity Analysis}
\label{sec:UQ}
The previous section shows that different HFX affect the calculated ToF. In this section, we use the Monte Carlo method to estimate the range of the ToF given a confidence level, followed by a sensitivity analysis to determine which parameter contributes more to the variance of ToF.
